# Who were the winners?
```{r}
# Load libraries 
library(dbplyr)
library(tidyverse)
library(DBI)
library(duckdb)
```

## DB Connection and Load Tables
```{r}
# Establish db connection 
conn <- DBI::dbConnect(duckdb::duckdb(),
                       dbdir = "database/database.duckdb")
# View tables
DBI::dbListTables(conn)

# Load relevant tables for analyses
personnel_db <- tbl(conn, "Personnel") # For observer name
bird_nests_db <- tbl(conn, "Bird_eggs") # For Egg_num, use Nest_ID
bird_nests_db <- tbl(conn, "Bird_nests") # For Nest_ID and Observer link 
```

## SQL Query 
```{sql}
SELECT Personnel.Name, COUNT(*) AS total_eggs
FROM Bird_nests
JOIN Bird_eggs ON Bird_nests.Nest_ID = Bird_eggs.Nest_ID
JOIN Personnel ON Bird_nests.Observer = Personnel.Abbreviation
GROUP BY Personnel.Name
ORDER BY egg_count DESC
LIMIT 3;
```

## R: Collect()
```{r}
# R translation of SQL query 
result <- bird_nests_db %>%
  inner_join(bird_eggs_db, by = "Nest_ID") %>%
  inner_join(personnel_db, by = c("Observer" = "Abbreviation")) %>%
  group_by(Name) %>%
  summarize(total_eggs = n()) %>%
  arrange(desc(total_eggs)) %>%
  head(3) %>%
  collect()

# View 
View(result)
```

## R: Show_query()
```{r}
bird_nests_db %>%
  inner_join(bird_eggs_db, by = "Nest_ID") %>%
  inner_join(personnel_db, by = c("Observer" = "Abbreviation")) %>%
  group_by(Name) %>%
  summarize(total_eggs = n()) %>%
  arrange(desc(total_eggs)) %>%
  head(3) %>% 
  show_query()
```

## Questions
1. I created a seperate table `result` in order to store the query. This result was able to be seen by using the view() function. `dbplyr` only materializes the query into the R environment using the `collect()` function. 
2. Yes, for both instances you need to limit to the first 3 rows after arranging in descneding order. This is done with `head(3)` in R and `LIMIT 3` in SQL. 

### Close connection
```{r}
DBI::dbDisconnect(conn, shutdown = TRUE)
```
